---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "JP"
date: "3 de noviembre de 2016"
output: ioslides_presentation
---


## News Word Cloud

This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

The app developed for the first part of the assignment demo is avalilable at: 

Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/jpmoraga/Varios/tree/master/ThePress1


## Slide with R Output

The data used for this App was downloaded from the Machine Learning repository of the University of California.

- http://archive.ics.uci.edu/ml/machine-learning-databases/00359/NewsAggregatorDataset.zip

To download the data you should run the following code:

```{r Download data, eval=FALSE}
download.file(
  
"http://archive.ics.uci.edu/ml/machine-learning-databases/00359/NewsAggregatorDataset.zip",
              "YOUR FOLDER"
)

unzip("NewsAggregatorDataset.zip")
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

