---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Juan Pablo Moraga"
date: "3 de noviembre de 2016"
output: ioslides_presentation
---


## News Word Cloud

This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

The app developed for the first part of the assignment demo is avalilable at: 

- https://jpmoraga.shinyapps.io/news_word_cloud/

*The App takes between 30 seconds and a minute in generate de word cloud.* 

Source code for ui.R and server.R files are available on the GitHub repo:

- https://github.com/jpmoraga/Varios/tree/master/News%20Word%20Cloud


## Data base source

The data used for this App was downloaded from the Machine Learning repository of the University of California.

- http://archive.ics.uci.edu/ml/machine-learning-databases/00359/NewsAggregatorDataset.zip

To download the data you should run the following code:

```{r Download data, eval=FALSE}
download.file(
  
"http://archive.ics.uci.edu/ml/machine-learning-databases/00359/NewsAggregatorDataset.zip",
              "YOUR FOLDER"
)

unzip("NewsAggregatorDataset.zip")
```

## Example

As an example, if you select this filters:

- Date: 2014-03-19
- Publisher: NASDAQ
- Color palette: Accent
- Font Face: Bold
- Font Family: Script
- Max Words: 42

Your output should be this wordcloud:

## Word Cloud

```{r echo=FALSE, comment=NULL, message=FALSE, error=FALSE, warning=FALSE}

     
      library(devtools)
      library(digest)
      library(shinyapps)
      library(shiny)
      library(NLP)
      library(tm)
      library(RColorBrewer)
      library(wordcloud)
      library(plyr)
      NC <- read.csv("newsCorpora.csv", header = FALSE, sep = "\t")
      
      
      names(NC) <- c("ID","TITLE", "URL", "PUBLISHER", "CATEGORY", "STORY", "HOSTNAME", "TIMESTAMP")
      
      
      T <- NC[NC$PUBLISHER %in% c("Reuters", "Huffington Post", "Businessweek", "Daily Mail", "Contactmusic.com", "NASDAQ"),c("ID","TITLE","PUBLISHER", "CATEGORY", "TIMESTAMP")]
      
      
      T$TIMESTAMP <- as.Date(as.POSIXct(T$TIMESTAMP/1000, origin = "1970-01-01"))

      
      
      T1 <- T[as.Date(T$TIMESTAMP,"%Y-%m-%d") == "2014-03-19" & T$PUBLISHER == "NASDAQ", ]
      
      
      T2 <- as.vector(T1$TITLE)
      
      t_corp <- VCorpus(VectorSource(T2))
      
      t_corp1 <- tm_map(t_corp,removePunctuation)
      
      t_corp2 <- tm_map(t_corp1, removeNumbers)
      
      t_corp3 <- tm_map(t_corp2, content_transformer(tolower)) 
      
      t_corp4 <- tm_map(t_corp3,removeWords, c(stopwords("en"), "update"))
      
      t_corp5 <- TermDocumentMatrix(t_corp4)
      
      m <- as.matrix(t_corp5)
      
      v <- sort(rowSums(m),decreasing=TRUE)
      
      DF <- data.frame(word = names(v),freq=v)
      
      DF$Len <- nchar(as.vector(row.names(DF)))
      
      Words <- subset(DF, Len < 20 & Len > 3, -Len)
      ##x <- colnames(airquality)
      
      wordcloud(row.names(Words), freq = v, scale=c(5,.6), min.freq = 3, max.words = 42, colors = brewer.pal(8,"Accent"), vfont = c("script","bold"), rot.per=.3)

```

